Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-01-04 Latex/journal_v1/V2/pr.tex
change system model image
journal okey

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{Drawing11.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{r=1}^{R}\sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

The total power cost of O-RUs for transmitting data to UE is depicted as follow
P_{tot} = \sum_{r=1}^{R}P_r

@@

The aim of this paper is to maximize the benefits and minimize the cost. So our goal is to maximize sum rate of all UEs and minimize the total cost of the system with the presence of constraints which is written as follow,

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}- \eta(P_{tot}+ \varphi \phi_{tot}) \ \\

@@

&p_{r,u_i}^{k,s}  \geq 0  \quad \forall v,\forall i,\forall r,\forall s, \forall k,\label{c12} \\

@@

& \phi_{s} \leq \phi_{max}, \quad \forall s \label{c19} \\

>>>>

\begin{figure}
  \centering
    \includegraphics[scale = 0.4]{draw1.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th}$ application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_2,i)}^{u,r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

%The total power cost of O-RUs for transmitting data to UE is depicted as follow
%\begin{equation}
%P_{tot} = \sum_{r=1}^{R}P_r
%\end{equation}

@@

The aim of this paper is to maximize the sum rate of all UEs  with the presence of constraints which is written as follow,

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\

@@

&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\

@@

& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
